---
title: "p8105_hw1_qz2493.Rmd"
author: "Qingyue Zhuo"
date: "2022-09-20"
output:
  pdf_document: default
  html_document: default
---
```{r}
library(tidyverse)
library(ggplot2)
```

Problem 1

The variables of the data set are "species", "island" ,"bill_length_mm", "bill_depth_mm", "flipper_length_mm", "body_mass_g", "sex", "year"."species" has three levels: Adelie, Chinstrap, and Gentoo; "island" has three levels:  Biscoe, Dream and Torgersen; "sex" is a binary variable with two levels: male and female.
The data set has 344 rows and 8 columns.
The mean flipper length is 200.9152mm after excluding the missing value NAs.

```{r}
data("penguins", package = "palmerpenguins")
names(penguins)
levels(penguins$species)
levels(penguins$island)
nrow(penguins)
ncol(penguins)
mean(penguins$flipper_length_mm, na.rm = TRUE)

ggplot(penguins, aes(x = flipper_length_mm, y = bill_length_mm, col = species)) + geom_point()

ggsave("Penguins_scatter_plot.pdf")
```

Problem 2

The mean of numeric and logical vectors work, while the mean for character and factor vectors do not work.

```{r}

hw2_df = tibble(
  vec_numeric = rnorm(n = 10),
  vec_logical = vec_numeric > 0,
  vec_char = c('a','b','c','d','e','f','g','h','i','j'),
  vec_factor = factor(c("tall", "grande", "venti", "tall", "grande", "venti", "tall", "grande", "venti", "tall" ))
)

mean(pull(hw2_df,vec_numeric))
mean(pull(hw2_df,vec_logical))
mean(pull(hw2_df,vec_char))
mean(pull(hw2_df,vec_factor))

```

