---
title: "p8105_hw1_qz2493.Rmd"
author: "Qingyue Zhuo"
date: "2022-09-20"
output:
  pdf_document: default
  html_document: default
---
```{r}
library(tidyverse)
library(ggplot2)
```

Problem 1

```{r}
data("penguins", package = "palmerpenguins")
```

The variables of the data set are `r names(penguins)`. "Species" has three levels:`r levels(penguins$island)` ; "island" has three levels:  `r levels(penguins$island)`; "sex" is a binary variable with two levels: `r levels(penguins$sex)`.
The data set has `r nrow(penguins)` and `r ncol(penguins)` columns.
The mean flipper length is `r round(mean(penguins$flipper_length_mm, na.rm = TRUE),2)` mm after excluding the missing value NAs.


```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, col = species)) + geom_point()

ggsave("Penguins_scatter_plot.pdf")
```

Problem 2

```{r}

hw2_df = tibble(
  vec_numeric = rnorm(n = 10),
  vec_logical = vec_numeric > 0,
  vec_char = c('a','b','c','d','e','f','g','h','i','j'),
  vec_factor = factor(c("tall", "grande", "venti", "tall", "grande", "venti", "tall", "grande", "venti", "tall" ))
)

mean(pull(hw2_df,vec_numeric))
mean(pull(hw2_df,vec_logical))
mean(pull(hw2_df,vec_char))
mean(pull(hw2_df,vec_factor))

```

The mean of numeric and logical vectors work, while the mean of character and factor vectors do not work.

```{r eval = FALSE}
as.numeric(pull(hw2_df,vec_logical))
as.numeric(pull(hw2_df,vec_char))
as.numeric(pull(hw2_df,vec_factor))
```

After applying the as.numeric function, the logical variable has two values 0 and 1; factor variable has three values 1, 2 and 3; while character variable turns into "NA"s. Logical variable only has two outcomes and can be counted as 0 and 1 in calculating mean. Factor variable is categorical variable, although it can be converted into numeric values 1, 2 and 3 but it means group 1, group 2 and group 3 therefore it makes no sense in calculating the mean. Character variable cannot be even be turned into numeric, therefore it doesn't have a mean.